### 2022-11-28 dissertation/chapters/08-results.tex
♻️ (chapters 6 and 8): Restore
🚧 (final-review): Chapter 7 WIP

	\item \textbf{Section \ref{sec:results:standalone}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics on all datasets. Three variants of the \acs{BHH} are included in these results. These include the baseline configuration, as well as a configuration that only includes gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes meta-heuristics in the \index{heuristic pool}heuristic pool.

@@

This section provides the empirical results for the experimental group that compares the performance of the \acs{BHH} to the performance of the individual, standalone, low-level heuristics. Detailed discussions and illustrations follow. As a reminder, the set of low-level heuristics includes a number of gradient-based heuristics and a number of meta-heuristics. Three variants of the \acs{BHH} is included in the experiment, including the \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics (denoted bhh\_all), the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics (denoted bhh\_gd), and finally, the \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics (denoted bhh\_mh).

@@

\begin{table}[htb]
	\centering
	\caption{Empirical results showing average test loss and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
	\label{tab:results:heuristic_pool:metrics:loss}%
	\par\bigskip
	\resizebox{0.8\textwidth}{!}{
		\begin{tabular}{r|lll}
			                             & \multicolumn{3}{c}{\textbf{Heuristic Pool - Average Test Loss}}                                                                                                                     \\
			\midrule
			\textbf{dataset}             & \multicolumn{1}{c}{\textbf{all}}                                & \multicolumn{1}{c}{\textbf{gd}}                         & \multicolumn{1}{c}{\textbf{mh}}                         \\
			\midrule
			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.088)            & \cellcolor[rgb]{ .388,  .745,  .482}2.0125 ($\pm$0.068) & \cellcolor[rgb]{ .973,  .412,  .42}2.2942 ($\pm$0.055)  \\
			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)          & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2637 ($\pm$0.007) \\
			\textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 ($\pm$0.065)            & \cellcolor[rgb]{ .388,  .745,  .482}0.2164 ($\pm$0.005) & \cellcolor[rgb]{ .973,  .412,  .42}0.2562 ($\pm$0.011)  \\
			\textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}0.0651 ($\pm$0.02)             & \cellcolor[rgb]{ .388,  .745,  .482}0.0545 ($\pm$0.005) & \cellcolor[rgb]{ .973,  .412,  .42}0.1179 ($\pm$0.006)  \\
			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034)         & \cellcolor[rgb]{ 1,  .922,  .518}0.169 ($\pm$0.025)     & \cellcolor[rgb]{ .973,  .412,  .42}0.4891 ($\pm$0.077)  \\
			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)           & \cellcolor[rgb]{ .388,  .745,  .482}0.8976 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .922,  .518}0.9137 ($\pm$0.008)    \\
			\textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)            & \cellcolor[rgb]{ .973,  .412,  .42}0.1056 ($\pm$0.008)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1043 ($\pm$0.009) \\
			\textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}0.081 ($\pm$0.069)           & \cellcolor[rgb]{ .388,  .745,  .482}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ 1,  .922,  .518}0.0621 ($\pm$0.038)    \\
			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017)         & \cellcolor[rgb]{ 1,  .922,  .518}0.0951 ($\pm$0.015)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1169 ($\pm$0.019)  \\
			\textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2411 ($\pm$0.295)            & \cellcolor[rgb]{ .973,  .412,  .42}0.3729 ($\pm$1.119)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1809 ($\pm$0.164) \\
			\textbf{mushroom}            & \cellcolor[rgb]{ 1,  .922,  .518}0.0052 ($\pm$0.012)            & \cellcolor[rgb]{ .388,  .745,  .482}0.0009 ($\pm$0.001) & \cellcolor[rgb]{ .973,  .412,  .42}0.0774 ($\pm$0.02)   \\
			\textbf{parkinsons}          & \cellcolor[rgb]{ 1,  .922,  .518}0.0587 ($\pm$0.003)            & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.0658 ($\pm$0.003)  \\
			\textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}0.2359 ($\pm$0.102)            & \cellcolor[rgb]{ .973,  .412,  .42}0.2454 ($\pm$0.134)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1947 ($\pm$0.014) \\
			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0827 ($\pm$0.026)         & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .973,  .412,  .42}1.1666 ($\pm$0.03)   \\
		\end{tabular}%

@@

Table \ref{tab:results:reselection:metrics:rank} shows that larger reselection intervals are mostly preferred. The overall normalised average rank is given at the bottom of the table and supports this finding. This outcome can be explained as follows. A larger reselection interval gives the low-level \index{heuristic}heuristics more time to execute, resulting in smoother update steps and provides an opportunity for the \acs{BHH} to gather more evidence of the current selection of \index{heuristic}heuristics' performance in the performance log. Both of these effects allow the \acs{BHH} to select better \index{heuristic}heuristics during training. This is further supported by the findings from Sections \ref{sec:results:standalone} and \ref{sec:results:heuristic_pool}, that show that gradient-based \index{heuristic}heuristics generally yield the best performance. Most of the gradient-based \index{heuristic}heuristics that are included in the \index{heuristic pool }heuristic pool implement exponentially averaged state parameters in order to produce smooth update steps. If reselection occurs too frequently these exponentially averaged state parameters do not yield smooth update steps. This is further supported by the inclusion of meta-heuristics such as \acp{GA} and \acs{DE}, which recombine state parameters.

@@

\begin{table}[htb]
	\centering
	\caption{Empirical results showing average rank and statistics for discounted rewards toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
	\label{tab:results:discounted_rewards:metrics:rank}%
	\par\bigskip
	\resizebox{0.7\textwidth}{!}{
		\begin{tabular}{rcc}
			\multicolumn{1}{r|}{}                             & \multicolumn{2}{c}{\textbf{Discounted Rewards - Average Rank}}                                                           \\
			\midrule
			\multicolumn{1}{r|}{\textbf{dataset}}             & \textbf{false}                                                 & \textbf{true}                                           \\
			\midrule
			\multicolumn{1}{r|}{\textbf{abalone}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4914 ($\pm$0.5)          & \cellcolor[rgb]{ .973,  .412,  .42}1.5086 ($\pm$0.5)    \\
			\multicolumn{1}{r|}{\textbf{air quality}}         & \cellcolor[rgb]{ .388,  .745,  .482}1.4613 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5387 ($\pm$0.499)  \\
			\multicolumn{1}{r|}{\textbf{bank}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5161 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4839 ($\pm$0.5)   \\
			\multicolumn{1}{r|}{\textbf{bike}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5011 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4989 ($\pm$0.5)   \\
			\multicolumn{1}{r|}{\textbf{car}}                 & \cellcolor[rgb]{ .388,  .745,  .482}1.428 ($\pm$0.495)         & \cellcolor[rgb]{ .973,  .412,  .42}1.572 ($\pm$0.495)   \\
			\multicolumn{1}{r|}{\textbf{diabetic}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4699 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5301 ($\pm$0.499)  \\
			\multicolumn{1}{r|}{\textbf{fish toxicity}}       & \cellcolor[rgb]{ .973,  .412,  .42}1.5011 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4989 ($\pm$0.5)   \\
			\multicolumn{1}{r|}{\textbf{forest fires}}        & \cellcolor[rgb]{ .388,  .745,  .482}1.4742 ($\pm$0.5)          & \cellcolor[rgb]{ .973,  .412,  .42}1.5258 ($\pm$0.5)    \\
			\multicolumn{1}{r|}{\textbf{housing}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4237 ($\pm$0.494)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5763 ($\pm$0.494)  \\
			\multicolumn{1}{r|}{\textbf{iris}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5903 ($\pm$0.492)         & \cellcolor[rgb]{ .388,  .745,  .482}1.4097 ($\pm$0.492) \\
			\multicolumn{1}{r|}{\textbf{mushroom}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.3946 ($\pm$0.489)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5806 ($\pm$0.494)  \\
			\multicolumn{1}{r|}{\textbf{parkinsons}}          & \cellcolor[rgb]{ .388,  .745,  .482}1.371 ($\pm$0.483)         & \cellcolor[rgb]{ .973,  .412,  .42}1.629 ($\pm$0.483)   \\
			\multicolumn{1}{r|}{\textbf{student performance}} & \cellcolor[rgb]{ .388,  .745,  .482}1.4398 ($\pm$0.497)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5602 ($\pm$0.497)  \\
			\multicolumn{1}{r|}{\textbf{wine quality}}        & \cellcolor[rgb]{ .973,  .412,  .42}1.557 ($\pm$0.497)          & \cellcolor[rgb]{ .388,  .745,  .482}1.443 ($\pm$0.497)  \\
			\midrule
			\multicolumn{1}{r|}{\textbf{avg rank}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4728 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5254 ($\pm$0.499)  \\
			\midrule
			\textbf{normalised avg rank}                      & \cellcolor[rgb]{ .388,  .745,  .482}1                          & \cellcolor[rgb]{ .973,  .412,  .42}2                    \\
		\end{tabular}%
	}
\end{table}%

>>>>

      \item \textbf{Section \ref{sec:results:standalone}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics on all datasets. Three variants of the \acs{BHH} are included in these results. These include the baseline configuration, as well as a configuration that only includes gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes \acp{MH} in the \index{heuristic pool}heuristic pool.

@@

This section provides the empirical results for the experimental group that compares the performance of the \acs{BHH} to the performance of the individual, standalone, low-level heuristics. Detailed discussions and illustrations follow. As a reminder, the set of low-level heuristics includes a number of gradient-based heuristics and a number of \acp{MH}. Three variants of the \acs{BHH} is included in the experiment, including the \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics (denoted bhh\_all), the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics (denoted bhh\_gd), and finally, the \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics (denoted bhh\_mh).

@@

      \caption{Empirical results showing average test loss and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
      \label{tab:results:heuristic_pool:metrics:loss}%
            \begin{tabular}{r|lll}
                                               & \multicolumn{3}{c}{\textbf{Heuristic Pool - Average Test Loss}}                                                                                                                     \\
                  \textbf{dataset}             & \multicolumn{1}{c}{\textbf{all}}                                & \multicolumn{1}{c}{\textbf{gd}}                         & \multicolumn{1}{c}{\textbf{mh}}                         \\
                  \textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.088)            & \cellcolor[rgb]{ .388,  .745,  .482}2.0125 ($\pm$0.068) & \cellcolor[rgb]{ .973,  .412,  .42}2.2942 ($\pm$0.055)  \\
                  \textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)          & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2637 ($\pm$0.007) \\
                  \textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 ($\pm$0.065)            & \cellcolor[rgb]{ .388,  .745,  .482}0.2164 ($\pm$0.005) & \cellcolor[rgb]{ .973,  .412,  .42}0.2562 ($\pm$0.011)  \\
                  \textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}0.0651 ($\pm$0.02)             & \cellcolor[rgb]{ .388,  .745,  .482}0.0545 ($\pm$0.005) & \cellcolor[rgb]{ .973,  .412,  .42}0.1179 ($\pm$0.006)  \\
                  \textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034)         & \cellcolor[rgb]{ 1,  .922,  .518}0.169 ($\pm$0.025)     & \cellcolor[rgb]{ .973,  .412,  .42}0.4891 ($\pm$0.077)  \\
                  \textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)           & \cellcolor[rgb]{ .388,  .745,  .482}0.8976 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .922,  .518}0.9137 ($\pm$0.008)    \\
                  \textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)            & \cellcolor[rgb]{ .973,  .412,  .42}0.1056 ($\pm$0.008)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1043 ($\pm$0.009) \\
                  \textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}0.081 ($\pm$0.069)           & \cellcolor[rgb]{ .388,  .745,  .482}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ 1,  .922,  .518}0.0621 ($\pm$0.038)    \\
                  \textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017)         & \cellcolor[rgb]{ 1,  .922,  .518}0.0951 ($\pm$0.015)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1169 ($\pm$0.019)  \\
                  \textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2411 ($\pm$0.295)            & \cellcolor[rgb]{ .973,  .412,  .42}0.3729 ($\pm$1.119)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1809 ($\pm$0.164) \\
                  \textbf{mushroom}            & \cellcolor[rgb]{ 1,  .922,  .518}0.0052 ($\pm$0.012)            & \cellcolor[rgb]{ .388,  .745,  .482}0.0009 ($\pm$0.001) & \cellcolor[rgb]{ .973,  .412,  .42}0.0774 ($\pm$0.02)   \\
                  \textbf{parkinsons}          & \cellcolor[rgb]{ 1,  .922,  .518}0.0587 ($\pm$0.003)            & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.0658 ($\pm$0.003)  \\
                  \textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}0.2359 ($\pm$0.102)            & \cellcolor[rgb]{ .973,  .412,  .42}0.2454 ($\pm$0.134)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1947 ($\pm$0.014) \\
                  \textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0827 ($\pm$0.026)         & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .973,  .412,  .42}1.1666 ($\pm$0.03)   \\

@@

Table \ref{tab:results:reselection:metrics:rank} shows that larger reselection intervals are mostly preferred. The overall normalised average rank is given at the bottom of the table and supports this finding. This outcome can be explained as follows. A larger reselection interval gives the low-level \index{heuristic}heuristics more time to execute, resulting in smoother update steps and provides an opportunity for the \acs{BHH} to gather more evidence of the current selection of \index{heuristic}heuristics' performance in the performance log. Both of these effects allow the \acs{BHH} to select better \index{heuristic}heuristics during training. This is further supported by the findings from Sections \ref{sec:results:standalone} and \ref{sec:results:heuristic_pool}, that show that gradient-based \index{heuristic}heuristics generally yield the best performance. Most of the gradient-based \index{heuristic}heuristics that are included in the \index{heuristic pool }heuristic pool implement exponentially averaged state parameters in order to produce smooth update steps. If reselection occurs too frequently these exponentially averaged state parameters do not yield smooth update steps. This is further supported by the inclusion of \acp{MH} such as \acp{GA} and \acs{DE}, which recombine state parameters.

@@

      \caption{Empirical results showing average rank and statistics for discounted rewards toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
      \label{tab:results:discounted_rewards:metrics:rank}%
      \resizebox{0.7\textwidth}{!}{
            \begin{tabular}{rcc}
                  \multicolumn{1}{r|}{}                             & \multicolumn{2}{c}{\textbf{Discounted Rewards - Average Rank}}                                                           \\
                  \multicolumn{1}{r|}{\textbf{dataset}}             & \textbf{false}                                                 & \textbf{true}                                           \\
                  \multicolumn{1}{r|}{\textbf{abalone}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4914 ($\pm$0.5)          & \cellcolor[rgb]{ .973,  .412,  .42}1.5086 ($\pm$0.5)    \\
                  \multicolumn{1}{r|}{\textbf{air quality}}         & \cellcolor[rgb]{ .388,  .745,  .482}1.4613 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5387 ($\pm$0.499)  \\
                  \multicolumn{1}{r|}{\textbf{bank}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5161 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4839 ($\pm$0.5)   \\
                  \multicolumn{1}{r|}{\textbf{bike}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5011 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4989 ($\pm$0.5)   \\
                  \multicolumn{1}{r|}{\textbf{car}}                 & \cellcolor[rgb]{ .388,  .745,  .482}1.428 ($\pm$0.495)         & \cellcolor[rgb]{ .973,  .412,  .42}1.572 ($\pm$0.495)   \\
                  \multicolumn{1}{r|}{\textbf{diabetic}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4699 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5301 ($\pm$0.499)  \\
                  \multicolumn{1}{r|}{\textbf{fish toxicity}}       & \cellcolor[rgb]{ .973,  .412,  .42}1.5011 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4989 ($\pm$0.5)   \\
                  \multicolumn{1}{r|}{\textbf{forest fires}}        & \cellcolor[rgb]{ .388,  .745,  .482}1.4742 ($\pm$0.5)          & \cellcolor[rgb]{ .973,  .412,  .42}1.5258 ($\pm$0.5)    \\
                  \multicolumn{1}{r|}{\textbf{housing}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4237 ($\pm$0.494)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5763 ($\pm$0.494)  \\
                  \multicolumn{1}{r|}{\textbf{iris}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5903 ($\pm$0.492)         & \cellcolor[rgb]{ .388,  .745,  .482}1.4097 ($\pm$0.492) \\
                  \multicolumn{1}{r|}{\textbf{mushroom}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.3946 ($\pm$0.489)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5806 ($\pm$0.494)  \\
                  \multicolumn{1}{r|}{\textbf{parkinsons}}          & \cellcolor[rgb]{ .388,  .745,  .482}1.371 ($\pm$0.483)         & \cellcolor[rgb]{ .973,  .412,  .42}1.629 ($\pm$0.483)   \\
                  \multicolumn{1}{r|}{\textbf{student performance}} & \cellcolor[rgb]{ .388,  .745,  .482}1.4398 ($\pm$0.497)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5602 ($\pm$0.497)  \\
                  \multicolumn{1}{r|}{\textbf{wine quality}}        & \cellcolor[rgb]{ .973,  .412,  .42}1.557 ($\pm$0.497)          & \cellcolor[rgb]{ .388,  .745,  .482}1.443 ($\pm$0.497)  \\
                  \multicolumn{1}{r|}{\textbf{avg rank}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4728 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5254 ($\pm$0.499)  \\
                  \textbf{normalised avg rank}                      & \cellcolor[rgb]{ .388,  .745,  .482}1                          & \cellcolor[rgb]{ .973,  .412,  .42}2                    \\

### 2022-11-28 dissertation/chapters/09-conclusion.tex
🚧 (final-review): Chapter 7 WIP

\begin{quotation}
      \noindent ``I am sorry to have made such a long speech, but I did not have time to make a shorter one.''
\end{quotation}
\begin{flushright}
      - Winston Churchill
\end{flushright}

This chapter provides a summary of the research that is done in this dissertation. The research objectives were set out in Chapter \ref{chap:introduction} and are concluded in this chapter. Furthermore, this chapter provides a summary of the results and findings from the empirical process and provides future research opportunities. The remainder of the chapter is structured as follows.

@@

Existing techniques from other problem domains were considered. \acs{RL}, meta-learning and probabilistic learning approached were considered. Bayesian probability theory showed promise. This research then set out to develop a novel high-level \index{heuristic}heuristic that utilises probability theory in an online learning setting to drive the automatic \index{heuristic}heuristic selection process. As such, the \acs{BHH} was conceptualised. The research objectives were defined and are summarised as follows.

@@

It was mentioned that the \acs{BHH}, implemented in this dissertation, does not implement a move-acceptance strategy that rejects heuristic progressions if they do not improve on the current best solution. Throughout the presentation of empirical results, it is recommended that this technique be investigated and implemented in further research.

@@

The main findings that were made for this experimental group are given as follows. Most of the training progression is made in the early stages of the training process. That leads to the conclusion that the \acs{BHH} has a small window from which it should learn and gain the most in the training process. After training has converged, the \acs{BHH} resets its concentration parameters and heuristic selection returns to the symmetric heuristic selection case. As such, the \acs{BHH} explores other heuristics in an attempt to further improve on the current best solution found. The test set was used as a validation set during training. Some overfitting can be observed as the \acs{BHH} tried finding better solutions on the train set, but at the cost of generalisation on the test set. Minor divergence of the training loss is observed as the \acs{BHH} explores other heuristics in an attempt to improve performance. Since no move-acceptance strategy, and no early stopping stategy was used, the \acs{BHH} could select heuristics that are sub-optimal. Future research opportunities should incorporate these aforementioned strategies.

@@

Throughout the presentation of the empirical results, it is mentioned that a move-acceptance strategy can be incorporated to reject \index{heuristic}heuristic progressions that do not improve on the current best solution found. This would eliminate any divergence in the training process as a result of selecting sub-optimal \index{heuristic}heuristics. Various different move-acceptance strategies can be developed and empirically tested.

@@

Similar to the move-acceptance strategy, throughout the presentation of the empirical results, it is mentioned that an early stopping strategy can be used to hault the training process if the performance does not improve for a number of steps. In this dissertation, a number of examples were presented where divergence of training loss occurred. Furthermore, a number of examples were presented where overfitting occurred. An early stopping strategy can help prevent such outcomes.

@@

All the source code, data, logs and analyses that were used in this dissertation, as well as the dissertation source itself, can be found at \url{https://github.com/arneschreuder/masters.ai}. The raw empirical data is made available on Google Cloud's BigQuery platform, under the project id \textit{masters-363209}.

>>>>

\begin{quotation}
      ``I am sorry to have made such a long speech, but I did not have time to make a shorter one.''
\end{quotation}
\begin{flushright}
      - Winston Churchill
\end{flushright}

This chapter provides a summary of the research that is done in this dissertation. The research objectives were set out in Chapter \ref{chap:introduction} and are concluded in this chapter. Furthermore, this chapter provides a summary of the results and findings from the empirical process and provides future research opportunities. The remainder of the chapter is structured as follows:

@@

Existing techniques from other problem domains were considered. \acs{RL}, meta-learning and probabilistic learning approached were considered. Bayesian probability theory showed promise. This research then set out to develop a novel high-level \index{heuristic}heuristic that utilises probability theory in an online learning setting to drive the automatic \index{heuristic}heuristic selection process. As such, the \acs{BHH} was conceptualised. The research objectives were defined and are summarised as follows:

@@

It was mentioned that the \acs{BHH}, implemented in this dissertation, does not implement a move acceptance strategy that rejects heuristic progressions if they do not improve on the current best solution. Throughout the presentation of empirical results, it is recommended that this technique be investigated and implemented in further research.

@@

The main findings that were made for this experimental group are given as follows. Most of the training progression is made in the early stages of the training process. That leads to the conclusion that the \acs{BHH} has a small window from which it should learn and gain the most in the training process. After training has converged, the \acs{BHH} resets its concentration parameters and heuristic selection returns to the symmetric heuristic selection case. As such, the \acs{BHH} explores other heuristics in an attempt to further improve on the current best solution found. The test set was used as a validation set during training. Some overfitting can be observed as the \acs{BHH} tried finding better solutions on the train set, but at the cost of generalisation on the test set. Minor divergence of the training loss is observed as the \acs{BHH} explores other heuristics in an attempt to improve performance. Since no move acceptance strategy, and no early stopping stategy was used, the \acs{BHH} could select heuristics that are sub-optimal. Future research opportunities should incorporate these aforementioned strategies.

@@

Throughout the presentation of the empirical results, it is mentioned that a move acceptance strategy can be incorporated to reject \index{heuristic}heuristic progressions that do not improve on the current best solution found. This would eliminate any divergence in the training process as a result of selecting sub-optimal \index{heuristic}heuristics. Various different move acceptance strategies can be developed and empirically tested.

@@

Similar to the move acceptance strategy, throughout the presentation of the empirical results, it is mentioned that an early stopping strategy can be used to hault the training process if the performance does not improve for a number of steps. In this dissertation, a number of examples were presented where divergence of training loss occurred. Furthermore, a number of examples were presented where overfitting occurred. An early stopping strategy can help prevent such outcomes.

@@

All the source code, data, logs and analyses that were used in this dissertation, as well as the dissertation source itself, can be found at \url{https://github.com/arneschreuder/masters}. The raw empirical data is made available on Google Cloud's BigQuery platform, under the project id \textit{masters-363209}.
